### 2007-01-19 Documentation/appendix.tex
*** empty log message ***

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Catalogue of {\sf AEDL}-Files}
\label{app:aedlfiles}
Along with the \GLOBES\ package comes a catalogue of pre-defined experiment \AEDL\ files for different
future experiments and different beam and detector technologies. These include the planned superbeam experiments
and their possible upgrades, different reactor experiment setups, different $\beta$-beam setups, and different 
neutrino factory setups. A complete list
of all pre-defined experiment files can be found in \tabl{experiments}. More detailed descriptions of the
corresponding files, the assumptions, requirements, and references are given in the following.

@@

\begin{center}
\begin{tabular}{lllllll} 
Experiment & File & Runtime & Power & Baseline & Detector & Mass \\ \hline \hline
T2K & {\tt T2K.glb} & 2~yr $\nu$/6~yr $\bar{\nu}$ & 0.77~MW & 295~km & WC & 22.5~kt \\ \hline
T2HK & {\tt T2HK.glb} & 4~yr $\nu$/4~yr $\bar{\nu}$ & 4~MW & 295~km & WC & 500~kt \\ \hline
NO$\nu$A & {\tt NOvA.glb} & 3~yr $\nu$/3~yr $\bar{\nu}$ & 1.12~MW & 812~km & TASD & 25~kt \\ \hline
SPL & {\tt SPL.glb} & 2~yr $\nu$/8~yr $\bar{\nu}$ & 4~MW & 130~km & WC & 500~kt \\ 
\end{tabular}
\end{center}

\subsection*{T2K -- {\tt T2K.glb}}

@@

sample stays {\tt chiSpectrumTilt}. Note, that otherwise the free normalization would be swiched off and all events from

@@

\subsection*{T2HK -- {\tt T2HK.glb}}

@@

\subsection*{NO$\nu$A -- {\tt NOvA.glb}}

The \NOVA\ experiment can be simulated with the file {\tt NOvA.glb}. The description of the disapperance 
channels is taken from \cite{Yang_2004} and the description of the appearance channels follows 
the proposal \cite{Ambats:2004js}. These references
should be cited if the file {\tt NOvA.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt NOvA.glb}, the following additional files are required: 
\bi
\item {\tt NOvAplus.dat} (NuMI neutrino flux -- $\nu_\mu$)
\item {\tt NOvAminus.dat} (NuMI neutrino flux -- $\bar{\nu}_\mu$)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
The \NOVA\ experiment uses a neutrino beam from the Fermilab NuMI beamline. The target power is 
1.12~MV which results in $10^{21}$~pot~$\mathrm{yr^{-1}}$ and 3~years $\nu$-running and 3~years $\bar{\nu}$-running 
is assumed. The fiducial mass of the Totally Liquid Scintillator Detector (TASD) is taken to be 
$\mathrm{m_{det} = 25 \,kt}$ at a baseline of L~=~812~km approximately 12~km off-axis to the beamline. The
energy resolution is $\mathrm{\sigma_e=10 \% \cdot \sqrt{E}}$ for electrons and  $\mathrm{\sigma_e=5 \% \cdot \sqrt{E}}$
for muons. The following rules are defined within {\tt NOvA.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance (+)} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.8 \, \otimes \, (\nu_\mu\rightarrow\nu_\mu)_{\mathrm{CC}}$ & & 0.05 & 0.025 \\
 & & & & \\
Background & $0.0015 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & & 0.05 & 0.025 \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (+)} & & \\ \hline
Signal & $0.24 \, \otimes \, (\nu_\mu \rightarrow \nu_e)_\mathrm{CC}$ & & 0.05 & 0.025\\
 & & & & \\
Background & $0.0015 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & $1.0\cdot 10^{-4} \, \otimes \,
(\nu_\mu\rightarrow\nu_\mu)_{\mathrm{CC}}$ & 0.05 & 0.025 \\
Beam background & $0.12 \, \otimes \, (\nu_e\rightarrow \nu_e)_\mathrm{CC}$ & & 0.05 & 0.025 \\ \hline \hline
\multicolumn{3}{|l|}{Disappearance (--)} &  &  \\ \hline
Signal & $0.8 \, \otimes \, (\bar{\nu}_\mu\rightarrow\bar{\nu}_\mu)_{\mathrm{CC}}$ & & 0.05 & 0.025 \\
 & & & & \\
Background & $0.0015 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.05 & 0.025 \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (--)} & & \\ \hline
Signal & $0.37 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_e)_\mathrm{CC}$ & & 0.05 & 0.025\\
 & & & & \\
Background & $0.0037 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $1.0\cdot 10^{-4} \, \otimes \,
(\bar{\nu}_\mu\rightarrow\bar{\nu}_\mu)_{\mathrm{CC}}$ & 0.05 & 0.025 \\
Beam background & $0.12 \, \otimes \, (\bar{\nu}_e\rightarrow \bar{\nu}_e)_\mathrm{CC}$ & & 0.05 & 0.025 \\ \hline \hline
\end{tabular}
\end{center}

\subsection*{SPL - {\tt SPL.glb}}

The \SPL\ experiment can be simulated with the file {\tt SPL.glb}. This file was used in \cite{Campagne:2006yx}
and follows the experiment description from \cite{Mezzetto:2003mm, Campagne:2004wt}. These references
should be cited if the file {\tt SPL.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt SPL.glb}, the following additional files are required: 
\bi
\item {\tt SPLplus.dat} (neutrino flux from CERN -- $\nu_\mu$)
\item {\tt SPLminus.dat} (neutrino flux from CERN -- $\bar{\nu}_\mu$)
\item {\tt Mig\_WC\_numu.dat} (migration matrix -- $\nu_\mu$)
\item {\tt Mig\_WC\_numubar.dat} (migration matrix -- $\bar{\nu}_\mu$)
\item {\tt Mig\_WC\_nue.dat} (migration matrix -- $\nu_e$)
\item {\tt Mig\_WC\_nuebar.dat} (migration matrix -- $\bar{\nu}_e$)
\item {\tt XCC\_spl.dat} (charged current cross sections)
\item {\tt XNC\_spl.dat} (neutral current cross sections)
\ei
The \SPL\ experiment uses a neutrino beam from the CERN to Fr\'{e}jus. The target power is 
4~MV and 2~years $\nu$-running and 8~years $\bar{\nu}$-running 
is assumed. The fiducial mass of the Water Cerenkov detector is taken to be 
$\mathrm{m_{det} = 500 \,kt}$ at a baseline of L~=~130~km. The energy resolution is introduced manually by
four migration matrices (for $\nu_e , \bar{\nu}_e ,\nu_{\mu} ,\bar{\nu}_\mu$) that describe energy smearing 
due to Fermi Motion. The following rules are defined within {\tt SPL.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance (+)} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\nu_\mu\rightarrow\nu_\mu)_{\mathrm{CC}}$ & (energy dep. efficiency) & 0.02 & $10^{-4}$\\
 & &  & &\\
Background & $4.3\cdot 10^{-5} \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & & 0.02 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (+)} &  & \\ \hline
Signal & $0.707 \, \otimes \, (\nu_\mu\rightarrow \nu_e)_\mathrm{CC}$ & & 0.02 & $10^{-4}$\\
&&&&\\
Background & $6.5\cdot 10^{-4} \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & $5.4\cdot 10^{-4} \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\
 & $0.7 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_e )_\mathrm{CC}$ & & 0.02 &  $10^{-4}$ \\
Beam Background & $0.677 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_e )_\mathrm{CC}$ & $0.707 \, \otimes \, (\nu_e \rightarrow \nu_e )_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\ \hline \hline
\multicolumn{3}{|l|}{Disappearance (--)} & & \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_\mu\rightarrow\bar{\nu}_\mu)_{\mathrm{CC}}$ & (energy dep. efficiency) & 0.02 & $10^{-4}$\\
 & &  & &\\
Background & $4.3\cdot 10^{-5} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & & 0.02 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (--)} &  & \\ \hline
Signal & $0.677 \, \otimes \, (\bar{\nu}_\mu\rightarrow \bar{\nu}_e)_\mathrm{CC}$ & & 0.02 & $10^{-4}$\\
&&&&\\
Background & $0.0025 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $5.4\cdot 10^{-4} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\
 & $0.7 \, \otimes \, (\nu_\mu \rightarrow \nu_e )_\mathrm{CC}$ & & 0.02 &  $10^{-4}$ \\
Beam Background & $0.677 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_e )_\mathrm{CC}$ & $0.707 \, \otimes \, (\nu_e \rightarrow \nu_e )_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{lllllll} 
Experiment & File & Runtime & th. Power & Baseline & Det. & Mass \\ \hline \hline
Small & {\tt Reactor1.glb} & 5~yr $\bar{\nu}$ & 4~GW & 1.7~km & LS & 20~t \\ \hline
Large & {\tt Reactor.glb} & 8~yr $\bar{\nu}$ & 10~GW & 1.7~km & LS & 100~t \\ \hline
DoubleCHOOZ & {\tt D-Chooz\_near.glb} & 5~yr $\bar{\nu}$ & 2$\times$4.2~GW & 0.1~km & LS & 10.16~t \\ 
 & {\tt D-Chooz\_far.glb} & 5~yr $\bar{\nu}$ & 2$\times$4.2~GW & 1.05~km & LS & 10.16~t \\ 
\end{tabular}
\end{center}

\subsection*{Small Reactor Experiment -- {\tt Reactor1.glb}}

The file {\tt Reactor1.glb} allows to simulate a small $\bar{\nu}_e$-disappearance reactor experiment. The basic
version of this file was used within \cite{Huber:2003pm} which should be cited if the file {\tt Reactor1.glb} is
used for a scientific publication or a talk. For calculations that involve {\tt Reactor1.glb}, the following
additional files are required:
\bi
\item {\tt Reactor.dat} (neutrino flux from reactor)
\item {\tt XCCreactor.dat} (charged current cross sections for low energies)
\ei
The neutrino source is the core of a nuclear power reactor. The integrated luminosity is assumed to be
$\mathrm{\mathcal{L} = 400 \,t \, GW\, yr}$, \eg\ a 20~t detector, a reactor with a thermal power of 4~GW
and a running period of 5 years. As detector technology, a liquid scintillator 
detector is assumed, a far detector at a baseline of L~=~1.7~km and a near detector which is
assumed to be identical to the far detector (maybe apart from the size) in order to minimize the impact of systematical uncertainties. The normalization error
used in the file {\tt Reactor1.glb} has to be considered as an effective error, receiving contributions from
individual uncertainties (see~\cite{Huber:2003pm}). The energy resolution is
$\mathrm{\sigma_e=5\%\cdot\sqrt{E_{vis}}}$ and the choice for {\tt @sigma\_function} is {\tt \#inverse\_beta}. The following rules are defined within {\tt Reactor1.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & \hspace{5.5cm} & 0.008 & 0.005\\
 & &  & &\\
Background & $5.8\cdot 10^{-5} \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_\mathrm{CC}$ & \hspace{5.5cm} &
$10^{-6}$ & $10^{-6}$ \\ \hline \hline 
\end{tabular}
\end{center}

\subsection*{Large Reactor Experiment -- {\tt Reactor2.glb}}

@@

\subsection*{DoubleCHOOZ -- {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb}}

The files {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb} allow to simulate the \DC\ reactor experiment in France. 
The basic versions of these files were used within \cite{Huber:2006vr}, which should be cited if the files 
{\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb} are
used for a scientific publication or a talk. For calculations that involve {\tt D-Chooz\_near.glb} and/or {\tt D-Chooz\_far.glb}, the following
additional files are required:
\bi
\item {\tt Reactor.dat} (neutrino flux from reactor)
\item {\tt XCCreactor.dat} (charged current cross sections for low energies)
\ei
The \DC\ experiment is located at the Chooz reactor complex, and the two reactor cores serve as $\bar{\nu}_e$
neutrino source, so the thermal power is $\mathrm{2\cdot4.2\,GW}$. Two identical liquid scintillator detectors
with a fiducial mass of $\mathrm{m_{det} = 10.16 \,t}$ are used as near and far detector. The far detector
is planned to be located in the {\sc Chooz} cavern at a baseline of L~=~1.05~km from the two reactor cores and
the near detector is assumed to be located at a distance of 0.1~km to the cores. The total running time of the
experiment is assumed to be 5 years. So, the integrated luminosity at the far detector yields $\mathrm{\mathcal{L} \approx
427 \,t \, GW\, yr}$.
Here, the total running time of 5 years is assumed within {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb}, so near
and far detector are assumed to start the mode of operation simultaneously. For the simulation of \DC\ and
considering a delayed start of data taking at the near detector the file {\tt D-Chooz\_near.glb} has to be
modified. The cancellation of systematical uncertainties is considered by the manual definition of a $\chi^2$
as described in \cite{Huber:2006vr} with the treatment of user-defined systematics as described in \Sec~\ref{sec:userchi}   
The energy resolution is
$\mathrm{\sigma_e=5\%\cdot\sqrt{E_{vis}}}$ and the choice for {\tt @sigma\_function} is {\tt \#inverse\_beta}. The following rules are defined within {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|c|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance} & $\sigma_\mathrm{flux}$ & $\sigma^N_\mathrm{fid}$ & $\sigma^F_\mathrm{fid}$ &
$\sigma^N_\mathrm{cal}$ & $\sigma^F_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & & 0.02 & 0.006 & 0.006 & 0.005 &
0.005 \\
 & & & & & & & \\
Background & neglected & (sys. dominates) & -- & -- & -- & -- & -- \\ \hline \hline 
\end{tabular}
\end{center}

@@

\subsection*{Higher Gamma Scenario -- {\tt BB\_350.glb}}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Catalogue of {\sf AEDL}-Files}
\label{app:aedlfiles}
%\index{norm}{glb files@{\tt glb}-files}

Along with the \GLOBES\ package comes a catalogue of pre-defined experiment \AEDL\ files for different
future experiments and different beam and detector technologies. These include the planned superbeam experiments
and their possible upgrades, different reactor experiment setups, different $\beta$-beam setups, and different 
neutrino factory setups. A complete list
of all pre-defined experiment files can be found in \tabl{experiments}. More detailed descriptions of the
corresponding files, the assumptions, requirements, and references are given in the following.

@@

\begin{center}
\begin{tabular}{lllllll}
\hline 
Experiment & File & Runtime & Power & Baseline & Detector & Mass \\ \hline \hline
T2K & {\tt T2K.glb} & 2~yr $\nu$/6~yr $\bar{\nu}$ & 0.77~MW & 295~km & WC & 22.5~kt \\ 
T2HK & {\tt T2HK.glb} & 4~yr $\nu$/4~yr $\bar{\nu}$ & 4~MW & 295~km & WC & 500~kt \\ 
NO$\nu$A & {\tt NOvA.glb} & 3~yr $\nu$/3~yr $\bar{\nu}$ & 1.12~MW & 812~km & TASD & 25~kt \\
SPL & {\tt SPL.glb} & 2~yr $\nu$/8~yr $\bar{\nu}$ & 4~MW & 130~km & WC & 500~kt \\ 
\hline
\end{tabular}
\end{center}

\subsection*{T2K -- {\tt T2K.glb}}
\index{aedl}{T2K.glb@{\tt T2K.glb}}

@@

sample stays {\tt chiSpectrumTilt}. Note, that otherwise the free normalization would be switched off and all events from

@@

\subsection*{T2HK -- {\tt T2HK.glb}}
\index{aedl}{T2HK.glb@{\tt T2HK.glb}}

@@

\subsection*{NO$\nu$A -- {\tt NOvA.glb}}
\index{aedl}{NOvA.glb@{\tt NOvA.glb}}

The \NOVA\ experiment can be simulated with the file {\tt NOvA.glb}. The description of the disappearance 
channels is taken from \cite{Yang_2004} and the description of the appearance channels follows 
the proposal \cite{Ambats:2004js}. These references
should be cited if the file {\tt NOvA.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt NOvA.glb}, the following additional files are required: 
\bi
\item {\tt NOvAplus.dat} (NuMI neutrino flux -- $\nu_\mu$)
\item {\tt NOvAminus.dat} (NuMI neutrino flux -- $\bar{\nu}_\mu$)
\item {\tt XCC.dat} (charged current cross sections)
\item {\tt XNC.dat} (neutral current cross sections)
\ei
The \NOVA\ experiment uses a neutrino beam from the Fermilab NuMI beamline. The source power is $10^{21}$~pot~$\mathrm{yr^{-1}}$, corresponding to a (naively computed) target power of
1.12~MW. For the running times, 3~years $\nu$-running and 3~years $\bar{\nu}$-running 
are assumed. The fiducial mass of the Totally Liquid Scintillator Detector (TASD) is taken to be 
$\mathrm{m_{det} = 25 \,kt}$ at a baseline of L~=~812~km approximately 12~km off-axis to the beamline. The
energy resolution is $\mathrm{\sigma_e=10 \% \cdot \sqrt{E}}$ for electrons and  $\mathrm{\sigma_e=5 \% \cdot \sqrt{E}}$
for muons. The following rules are defined within {\tt NOvA.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance (+)} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline
Signal & $0.8 \, \otimes \, (\nu_\mu\rightarrow\nu_\mu)_{\mathrm{CC}}$ & & 0.05 & 0.025 \\
 & & & & \\
Background & $0.0015 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & & 0.05 & 0.025 \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (+)} & & \\ \hline
Signal & $0.24 \, \otimes \, (\nu_\mu \rightarrow \nu_e)_\mathrm{CC}$ & & 0.05 & 0.025\\
 & & & & \\
Background & $0.0015 \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & $1.0\cdot 10^{-4} \, \otimes \,
(\nu_\mu\rightarrow\nu_\mu)_{\mathrm{CC}}$ & 0.05 & 0.025 \\
Beam background & $0.12 \, \otimes \, (\nu_e\rightarrow \nu_e)_\mathrm{CC}$ & & 0.05 & 0.025 \\ \hline \hline
\multicolumn{3}{|l|}{Disappearance (--)} &  &  \\ \hline
Signal & $0.8 \, \otimes \, (\bar{\nu}_\mu\rightarrow\bar{\nu}_\mu)_{\mathrm{CC}}$ & & 0.05 & 0.025 \\
 & & & & \\
Background & $0.0015 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & & 0.05 & 0.025 \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (--)} & & \\ \hline
Signal & $0.37 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_e)_\mathrm{CC}$ & & 0.05 & 0.025\\
 & & & & \\
Background & $0.0037 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $1.0\cdot 10^{-4} \, \otimes \,
(\bar{\nu}_\mu\rightarrow\bar{\nu}_\mu)_{\mathrm{CC}}$ & 0.05 & 0.025 \\
Beam background & $0.12 \, \otimes \, (\bar{\nu}_e\rightarrow \bar{\nu}_e)_\mathrm{CC}$ & & 0.05 & 0.025 \\ \hline \hline
\end{tabular}
\end{center}

\subsection*{SPL - {\tt SPL.glb}}
\index{aedl}{SPL.glb@{\tt SPL.glb}}

The \SPL\ experiment can be simulated with the file {\tt SPL.glb}. This file was used in \cite{Campagne:2006yx}
and follows the experiment description from \cite{Mezzetto:2003mm, Campagne:2004wt}. These references
should be cited if the file {\tt SPL.glb} is used for a scientific publication or a talk. For calculations that
involve {\tt SPL.glb}, the following additional files are required: 
\bi
\item {\tt SPLplus.dat} (neutrino flux from CERN -- $\nu_\mu$)
\item {\tt SPLminus.dat} (neutrino flux from CERN -- $\bar{\nu}_\mu$)
\item {\tt Mig\_WC\_numu.dat} (migration matrix -- $\nu_\mu$)
\item {\tt Mig\_WC\_numubar.dat} (migration matrix -- $\bar{\nu}_\mu$)
\item {\tt Mig\_WC\_nue.dat} (migration matrix -- $\nu_e$)
\item {\tt Mig\_WC\_nuebar.dat} (migration matrix -- $\bar{\nu}_e$)
\item {\tt XCC\_spl.dat} (charged current cross sections)
\item {\tt XNC\_spl.dat} (neutral current cross sections)
\ei
The \SPL\ experiment uses a neutrino beam from the CERN to Fr\'{e}jus. The target power is 
4~MW and 2~years $\nu$-running and 8~years $\bar{\nu}$-running 
is assumed. The fiducial mass of the Water Cerenkov detector is taken to be 
$\mathrm{m_{det} = 500 \,kt}$ at a baseline of L~=~130~km. The energy resolution is introduced manually by
four migration matrices (for $\nu_e , \bar{\nu}_e ,\nu_{\mu} ,\bar{\nu}_\mu$) that describe energy smearing 
due to Fermi Motion. The following rules are defined within {\tt SPL.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance (+)} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\nu_\mu\rightarrow\nu_\mu)_{\mathrm{CC}}$ & (energy dep. efficiency) & 0.02 & $10^{-4}$\\
 & &  & &\\
Background & $4.3\cdot 10^{-5} \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & & 0.02 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (+)} &  & \\ \hline
Signal & $0.707 \, \otimes \, (\nu_\mu\rightarrow \nu_e)_\mathrm{CC}$ & & 0.02 & $10^{-4}$\\
&&&&\\
Background & $6.5\cdot 10^{-4} \, \otimes \, (\nu_\mu \rightarrow \nu_x)_\mathrm{NC}$ & $5.4\cdot 10^{-4} \, \otimes \, (\nu_\mu \rightarrow \nu_\mu)_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\
 & $0.7 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_e )_\mathrm{CC}$ & & 0.02 &  $10^{-4}$ \\
Beam Background & $0.677 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_e )_\mathrm{CC}$ & $0.707 \, \otimes \, (\nu_e \rightarrow \nu_e )_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\ \hline \hline
\multicolumn{3}{|l|}{Disappearance (--)} & & \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_\mu\rightarrow\bar{\nu}_\mu)_{\mathrm{CC}}$ & (energy dep. efficiency) & 0.02 & $10^{-4}$\\
 & &  & &\\
Background & $4.3\cdot 10^{-5} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & & 0.02 & $10^{-4}$ \\ \hline \hline 
\multicolumn{3}{|l|}{Appearance (--)} &  & \\ \hline
Signal & $0.677 \, \otimes \, (\bar{\nu}_\mu\rightarrow \bar{\nu}_e)_\mathrm{CC}$ & & 0.02 & $10^{-4}$\\
&&&&\\
Background & $0.0025 \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_x)_\mathrm{NC}$ & $5.4\cdot 10^{-4} \, \otimes \, (\bar{\nu}_\mu \rightarrow \bar{\nu}_\mu)_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\
 & $0.7 \, \otimes \, (\nu_\mu \rightarrow \nu_e )_\mathrm{CC}$ & & 0.02 &  $10^{-4}$ \\
Beam Background & $0.677 \, \otimes \, (\bar{\nu}_e \rightarrow \bar{\nu}_e )_\mathrm{CC}$ & $0.707 \, \otimes \, (\nu_e \rightarrow \nu_e )_\mathrm{CC}$ & 0.02 & $10^{-4}$ \\ \hline \hline
\end{tabular}
\end{center}

@@

\begin{center}
\begin{tabular}{lllllll} 
\hline
Experiment & File & Runtime & th. Power & Baseline & Det. & Mass \\ \hline \hline
Small & {\tt Reactor1.glb} & 5~yr $\bar{\nu}$ & 4~GW & 1.7~km & LS & 20~t \\ 
Large & {\tt Reactor.glb} & 8~yr $\bar{\nu}$ & 10~GW & 1.7~km & LS & 100~t \\
Double Chooz & {\tt D-Chooz\_near.glb} & 5~yr $\bar{\nu}$ & 2$\times$4.2~GW & 0.1~km & LS & 10.16~t \\ 
 & {\tt D-Chooz\_far.glb} & 5~yr $\bar{\nu}$ & 2$\times$4.2~GW & 1.05~km & LS & 10.16~t \\ 
\hline 
\end{tabular}
\end{center}

\subsection*{Small Reactor Experiment -- {\tt Reactor1.glb}}
\index{aedl}{Reactor1.glb@{\tt Reactor1.glb}}

The file {\tt Reactor1.glb} allows to simulate a small $\bar{\nu}_e$-disappearance reactor experiment. The basic
version of this file was used within \cite{Huber:2003pm} which should be cited if the file {\tt Reactor1.glb} is
used for a scientific publication or a talk. For calculations that involve {\tt Reactor1.glb}, the following
additional files are required:
\bi
\item {\tt Reactor.dat} (neutrino flux from reactor)
\item {\tt XCCreactor.dat} (charged current cross sections for low energies)
\ei
The neutrino source is the core of a nuclear power reactor. The integrated luminosity is assumed to be
$\mathrm{\mathcal{L} = 400 \,t \, GW\, yr}$, such as for a 20~t detector, a reactor with a thermal power of 4~GW,
and a running period of 5 years. As detector technology, a liquid scintillator 
detector is assumed, a far detector at a baseline of L~=~1.7~km and a near detector which is
assumed to be identical to the far detector (maybe apart from the size) in order to minimize the impact of systematical uncertainties. The near detector is simulated implicitly by lower effective systematical errors,
and there are no external backgrounds assumed.
The normalization error
used in the file {\tt Reactor1.glb} has to be considered as an effective error, receiving contributions from
individual uncertainties (see \Ref~\cite{Huber:2003pm}). The energy resolution is
$\mathrm{\sigma_e=5\%\cdot\sqrt{E_{vis}}}$ and the choice for {\tt @sigma\_function} is {\tt \#inverse\_beta}. The following rules are defined within {\tt Reactor1.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance} & $\sigma_\mathrm{norm}$ & $\sigma_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & \hspace{5.5cm} & 0.008 & 0.005\\
 & &  & &\\
Background & $5.8\cdot 10^{-5} \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_\mathrm{CC}$ & \hspace{5.5cm} &
$10^{-6}$ & $10^{-6}$ \\ \hline \hline 
\end{tabular}
\end{center}

\subsection*{Large Reactor Experiment -- {\tt Reactor2.glb}}
\index{aedl}{Reactor2.glb@{\tt Reactor2.glb}}

@@

\subsection*{Double Chooz -- {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb}}
\index{aedl}{D-Chooznear.glb@{\tt D-Chooz\_near.glb}}
\index{aedl}{D-Choozfar.glb@{\tt D-Chooz\_far.glb}}

The files {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb} allow to simulate the \DC\ reactor experiment in France. They require user-defined systematics and \GLOBES\ 3.0 or higher, where the user-defined
systematics function can be found in the header of  {\tt D-Chooz\_near.glb} or {\tt example5.c}.
The basic versions of these files were used within \cite{Huber:2006vr}, which should be cited if the files 
{\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb} are
used for a scientific publication or a talk. For calculations that involve {\tt D-Chooz\_near.glb} and/or {\tt D-Chooz\_far.glb}, the following
additional files are required:
\bi
\item {\tt Reactor.dat} (neutrino flux from reactor)
\item {\tt XCCreactor.dat} (charged current cross sections for low energies)
\ei
The \DC\ experiment is located at the Chooz reactor complex, and the two reactor cores serve as $\bar{\nu}_e$
neutrino source, so the thermal power is $\mathrm{2\cdot4.2\,GW}$. Two identical liquid scintillator detectors
with a fiducial mass of $\mathrm{m_{det} = 10.16 \,t}$ are used as near and far detector. The far detector
is planned to be located in the {\sc Chooz} cavern at a baseline of L~=~1.05~km from the two reactor cores and
the near detector is assumed to be located at a distance of 0.1~km to the cores. The total running time of the
experiment is assumed to be 5 years. So, the integrated luminosity at the far detector yields $\mathrm{\mathcal{L} \approx
427 \,t \, GW\, yr}$.
Here, the total running time of 5 years is assumed within {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb}, so near
and far detector are assumed to start the mode of operation simultaneously. For the simulation of \DC\ and
considering a delayed start of data taking at the near detector the file {\tt D-Chooz\_near.glb} has to be
modified. The cancellation of systematical uncertainties is considered by the manual definition of a $\chi^2$
as described in \cite{Huber:2006vr} with the treatment of user-defined systematics as described in \Sec~\ref{sec:userchi}   
The energy resolution is
$\mathrm{\sigma_e=5\%\cdot\sqrt{E_{vis}}}$ and the choice for {\tt @sigma\_function} is {\tt \#inverse\_beta}. The following rules are defined within {\tt D-Chooz\_near.glb} and {\tt D-Chooz\_far.glb}: 
\begin{center}
\begin{tabular}{|l|ll|c|c|c|c|c|}
\hline \hline
\multicolumn{3}{|l|}{Disappearance} & $\sigma_\mathrm{flux}$ & $\sigma^N_\mathrm{fid}$ & $\sigma^F_\mathrm{fid}$ &
$\sigma^N_\mathrm{cal}$ & $\sigma^F_\mathrm{cal}$ \\ \hline 
Signal & $1.0 \, \otimes \, (\bar{\nu}_e\rightarrow\bar{\nu}_e)_{\mathrm{CC}}$ & & 0.02 & 0.006 & 0.006 & 0.005 &
0.005 \\
 & & & & & & & \\
Background & neglected & (sys. dominates) & -- & -- & -- & -- & -- \\ \hline \hline 
\end{tabular}
\end{center}

@@

\subsection*{Higher Gamma Scenario -- {\tt BB\_350.glb}}
\index{aedl}{BB350.glb@{\tt BB\_350.glb}}
